Containers and R---the Rockerverse and beyond

### 2019-12-07 manuscript.Rmd
Rename 'clients' to 'Interfaces for Docker in R' and some other minor changes.

@@

## Clients [Ellis Hughes, Robrecht Cannoodt @rcannood]

@@

# some functionalities might be missing. please add them if you find that any are missing!
package_functionalities <- tribble(
  ~package, ~id,
  "stevedore", c("api", "execute", "cloud", "images", "interact"), # build?
  "dockyard", c("dockerfile", "build", "execute"), # cloud?
  "dockermachine", c("install", "execute", "cloud", "interact"),
  "AzureContainers", c("execute", "cloud"),
  "babelwhale", c("execute", "interact", "othercontainers"),  
  "harbor", c("execute", "cloud", "images")
)

@@

knitr::kable(tab, escape = FALSE) %>% 
  # kable_styling(latex_options = "striped") %>%
  row_spec(0, angle = -90)
# don't print this table just yet, wait for this PR to be merged
# https://github.com/rstudio/rticles/pull/261
```

@@

<!-- From the github description:
The goal of **dockermachine** ([https://github.com/cboettig/dockermachine](https://github.com/cboettig/dockermachine)) is to provide a convenient interface to docker-machine from the R command line. This will allow R users to easily create, control, and destroy cloud instances across a wide variety of providers.
-->

<!-- From the cran description
**AzureContainers** ([https://cran.r-project.org/package=AzureContainers](https://cran.r-project.org/package=AzureContainers)) lets you build and deploy containerised services in R, using Docker and Kubernetes. For full functionality, you should have Docker installed, as well as the kubectl and helm commandline tools. Otherwise it is relatively lightweight, requiring neither Powershell nor Python.
-->

@@

<!-- from the github description
**harbor** ([https://github.com/wch/harbor](https://github.com/wch/harbor) is an R package for controlling docker containers on local and remote hosts.
-->

@@

DN conceived of the presented idea and \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team} and wrote the section about images for R distributions.
CB ..
RC ..
DE ..
ME ..
CF wrote the section about `r-online`, `dockerfiler`, `r-ci` and `r-db`.
BW ..
KR ..
NR ..
NX wrote the section on liftr.
LS \& NT wrote the section on Bioconductor.
All authors contributed to the discussion and outlook section and approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page} and \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history} provide a detailed view on the respective contributions.

>>>>

    email: robrecht@cannoodt.dev
  - name: Ellis Hughes

@@

## Interfaces for Docker in R [Ellis Hughes, Robrecht Cannoodt]

@@

# some functionalities might be missing. please add them if you find that any are missing!
package_functionalities <- tribble(
  ~package, ~id,
  "stevedore", c("api", "execute", "cloud", "images", "interact"), # build?
  "dockyard", c("dockerfile", "build", "execute"), # cloud?
  "dockermachine", c("install", "execute", "cloud", "interact"),
  "AzureContainers", c("build", "execute", "cloud"),
  "babelwhale", c("execute", "interact", "othercontainers"),  
  "harbor", c("execute", "cloud", "images")
)

@@

knitr::kable(tab, escape = FALSE) %>% 
  # kable_styling(latex_options = "striped") %>%
  row_spec(0, angle = -90)
```

@@

**dockermachine** ([https://github.com/cboettig/dockermachine](https://github.com/cboettig/dockermachine))
<!-- From the github description:
**dockermachine** ([https://github.com/cboettig/dockermachine](https://github.com/cboettig/dockermachine)) provides a convenient interface to docker-machine from the R command line. This will allow R users to easily create, control, and destroy cloud instances across a wide variety of providers.
-->

**AzureContainers** ([https://cran.r-project.org/package=AzureContainers](https://cran.r-project.org/package=AzureContainers))
<!-- From the cran description
 lets you build and deploy containerised services in R, using Docker and Kubernetes. For full functionality, you should have Docker installed, as well as the kubectl and helm commandline tools. Otherwise it is relatively lightweight, requiring neither Powershell nor Python.
-->

@@

**harbor** ([https://github.com/wch/harbor](https://github.com/wch/harbor)
<!-- from the github description
is an R package for controlling docker containers on local and remote hosts.
-->

@@

DN conceived of the presented idea and \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team} and wrote the section about images for R distributions.
CB ..
RC and RC wrote the section on interfaces for Docker in R.
DE ..
ME ..
CF wrote the section about `r-online`, `dockerfiler`, `r-ci` and `r-db`.
BW ..
KR ..
NR ..
NX wrote the section on liftr.
LS \& NT wrote the section on Bioconductor.
All authors contributed to the discussion and outlook section and approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page} and \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history} provide a detailed view on the respective contributions.
